Ionization of biological molecules by multicharged ions using the stoichiometric model

### 2019-12-02 submit_jpb/revsubmission/ionmol_stoi.tex
include Z scaling work

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figuras/atomicscaling.eps}
\caption{Reduced CDW total ionization cross section $\sigma_{\alpha}/Z^2$ 
of six atomic 
targets. The curves are labeled with the charge state corresponding to 
the six multicharged projectiles.}
\label{fig:atomscaling}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figuras/ener_mean.eps}
\caption{Mean emitted energy distribution for ionization by the impact 
of multicharged ions, given by Eq.~(\ref{40}). 
Solid lines for ion charges $+1$, $2+$, $4+$, $6+$ and $8+$, as indicated.
Dashed lines for $\bar{p}$ and dotted line for the Born approximation with $Z=1$.}
\label{fig:emittedener}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figuras/ang_mean.eps}
\caption{Mean emitted angle distribution for ionization by impact of
multicharged ions. Curves as in Fig.~\ref{fig:emittedener}.}
\label{fig:emittedang}
\end{figure*}

@@

For low energy electron emission, the angular dispersion is nearly 
isotropic~\cite{Rudd1992}.
A typical value for the ejection angle considered in the literature is 
$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
it is quite correct in the range of validity of the first Born 
approximation for any target. However, when a distorted wave approximation 
is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
in the intermediate energy region, as shown in Fig.~\ref{fig:emittedang}.
The higher the charge $Z$, the smaller 
$\overline{\theta}$ will be. Of course, this effect only holds at 
intermediate energies and not at high impact energies.

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figuras/adn1.eps}
\caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
of ion impact energy. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
for proton impact and $\square$~\cite{rahman2016} for electron impact 
with equivelocity conversion.}
\label{fig:crossDNA_1}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figuras/adn2.eps}
\caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
of ion impact energy. Experiments: proton impact on 
$\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
THF~\cite{wang2016}. Impact of $\ominus$ C$^{4+}$, 
$\oplus$ C$^{6+}$, O$^{6+}$, F$^{6+}$, and
$\otimes$ O$^{8+}$, F$^{8+}$ on 
uracil~\cite{agnihotri2012,agnihotri2013}. 
Symbols~$\rhd$~\cite{bug2017}, $\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} for electron impact with equivelocity 
conversion.}
\label{fig:crossDNA_2}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figuras/molscaling85.eps}
\caption{Scaled ionization cross section per weakly bound electron using
(a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
$\nu_{\alpha}^{\text{CDW}}$ for molecules listed in Table~\ref{tab:families}. 
For each band, the molecules are ordered from the smallest (top curve) to the
largest (bottom curve). Experiments: proton impact on 
\mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
$\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$ 
THF~\cite{wang2016}; electron impact on $\rhd$ pyrimidine~\cite{bug2017},
and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:newscaling}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.785\textwidth]{figuras/scale_ne.eps}
\caption{Ionization cross sections by the impact of protons at 0.5, 1,
and 2 MeV in terms of the number of active electrons given by Table~\ref{nn}.
Experiments: 
\mbox{\Large$\circ$}~adenine~\cite{iriki2011}, 
$\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
$\blacktriangle$ C$_2$H$_7$N, CH$_5$N, methane and ammonia~\cite{lynch1976},
\mbox{\scriptsize$\bigstar$} ammonia and H$_2$~\cite{rudd1985}, and 
\mbox{\Large$\bullet$} water~\cite{luna2007}.}
\label{fig:recta}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\textwidth]{figuras/levelsDNA.eps}
\caption{Theoretical molecular binding energies for adenine, cytosine, 
guanine, thymine, and uracil compared to those of atomic constituents.}
\label{fig:bindener}
\end{figure*}

@@

\begin{table*}[t]
\begin{center}
\begin{tabular}{|p{0.08\textwidth}|p{0.05\textwidth}|p{0.05\textwidth}|p{
0.05\textwidth}|p{0.05\textwidth}|p{0.19\textwidth}|}
\hline
Element & C & H & N & O & New stoichiometry \\
\hline
Adenine & +0.32 & +0.23 & --0.55 &       & 
C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
\hline
Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
C$_{3.93}$H$_{4.79}$N$_{3.14}$O$_{1.13}$ \\ 
\hline
Guanine & +0.46 & +0.20 & --0.58 & --0.36 & 
C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
\hline
Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
C$_{4.95}$H$_{5.81}$N$_{2.13}$O$_{2.13}$ \\ 
\hline
Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
C$_{3.92}$H$_{3.78}$N$_{2.15}$O$_{2.12}$ \\ 
\hline
\end{tabular}
\caption{Average effective Mulliken charge per atom $q_{\alpha}$, and 
new stoichiometric formula defined by Eq.~(\ref{eq:newstoi}) for five 
DNA molecules.}
\label{tab:newstoi}
\end{center}
\end{table*}

@@

\bibitem{Rudd1992} 
M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
%Electron production in proton collisions with atoms and molecules: energy distributions. 
Rev. Mod. Phys. \textbf{64}, 441--490 (1992).

>>>>

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{atomicscaling.eps}
\caption{Reduced CDW total ionization cross section $\sigma_{\alpha}/Z^2$ 
of six atomic 
targets. The curves are labeled with the charge state corresponding to 
the six multicharged projectiles.}
\label{fig:atomscaling}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{ener_mean.eps}
\caption{Mean emitted energy distribution for ionization by the impact 
of multicharged ions, given by Eq.~(\ref{40}). 
Solid lines for ion charges $+1$, $2+$, $4+$, $6+$ and $8+$, as indicated.
Dashed lines for $\bar{p}$ and dotted line for the Born approximation with $Z=1$.}
\label{fig:emittedener}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{ang_mean.eps}
\caption{Mean emitted angle distribution for ionization by impact of
multicharged ions. Curves as in Fig.~\ref{fig:emittedener}.}
\label{fig:emittedang}
\end{figure*}

@@

@@

It is a general belief~\cite{Rudd1992} that the 
angular dispersion of emitted electrons is nearly isotropic. This 
behavior is thought to be caused by the insignificant angular anisotropy 
of sub--50--eV yield. 
A typical value for the ejection angle considered in the literature is 
$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
it is quite correct in the range of validity of the first Born 
approximation for any target. However, when a distorted wave approximation 
is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
in the intermediate energy region, as shown in Fig.~\ref{fig:emittedang}.
The higher the charge $Z$, the smaller 
$\overline{\theta}$ will be. Of course, this effect only holds at 
intermediate energies and not at high impact energies.

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{adn1.eps}
\caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
of ion impact energy. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
for proton impact and $\square$~\cite{rahman2016} for electron impact 
with equivelocity conversion.}
\label{fig:crossDNA_1}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{adn2.eps}
\caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
of ion impact energy. Experiments: proton impact on 
$\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
THF~\cite{wang2016}. Impact of $\ominus$ C$^{4+}$, 
$\oplus$ C$^{6+}$, O$^{6+}$, F$^{6+}$, and
$\otimes$ O$^{8+}$, F$^{8+}$ on 
uracil~\cite{agnihotri2012,agnihotri2013}. 
Symbols~$\rhd$~\cite{bug2017}, $\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} for electron impact with equivelocity 
conversion.}
\label{fig:crossDNA_2}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{molscaling85.eps}
\caption{Scaled ionization cross section per weakly bound electron using
(a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
$\nu_{\alpha}^{\text{CDW}}$ for molecules listed in Table~\ref{tab:families}. 
For each band, the molecules are ordered from the smallest (top curve) to the
largest (bottom curve). Experiments: proton impact on 
\mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
$\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$ 
THF~\cite{wang2016}; electron impact on $\rhd$ pyrimidine~\cite{bug2017},
and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:newscaling}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.785\textwidth]{scale_ne.eps}
\caption{Ionization cross sections by the impact of protons at 0.5, 1,
and 2 MeV in terms of the number of active electrons given by Table~\ref{nn}.
Experiments: 
\mbox{\Large$\circ$}~adenine~\cite{iriki2011}, 
$\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
$\blacktriangle$ C$_2$H$_7$N, CH$_5$N, methane and ammonia~\cite{lynch1976},
\mbox{\scriptsize$\bigstar$} ammonia and H$_2$~\cite{rudd1985}, and 
\mbox{\Large$\bullet$} water~\cite{luna2007}.}
\label{fig:recta}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\textwidth]{levelsDNA.eps}
\caption{Theoretical molecular binding energies for adenine, cytosine, 
guanine, thymine, and uracil compared to those of atomic constituents.}
\label{fig:bindener}
\end{figure*}

@@

\begin{table*}[t!]
\begin{center}
\begin{tabular}{|p{0.08\textwidth}|p{0.05\textwidth}|p{0.05\textwidth}|p{
0.05\textwidth}|p{0.05\textwidth}|p{0.19\textwidth}|}
\hline
Element & C & H & N & O & New stoichiometry \\
\hline
Adenine & +0.32 & +0.23 & --0.55 &       & 
C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
\hline
Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
C$_{3.93}$H$_{4.79}$N$_{3.14}$O$_{1.13}$ \\ 
\hline
Guanine & +0.46 & +0.20 & --0.58 & --0.36 & 
C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
\hline
Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
C$_{4.95}$H$_{5.81}$N$_{2.13}$O$_{2.13}$ \\ 
\hline
Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
C$_{3.92}$H$_{3.78}$N$_{2.15}$O$_{2.12}$ \\ 
\hline
\end{tabular}
\caption{Average effective Mulliken charge per atom $q_{\alpha}$, and 
new stoichiometric formula defined by Eq.~(\ref{eq:newstoi}) for five 
DNA molecules.}
\label{tab:newstoi}
\end{center}
\end{table*}

@@

\bibitem{Rudd1992} 
M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
%Electron production in proton collisions with atoms and molecules: energy distributions. 
Rev. Mod. Phys. \textbf{64}, 44--490 (1992).

### 2019-12-02 submit_jpb/revsubmission_v2/ionmol_stoi.tex
include Z scaling work

It is a general belief~\cite{Rudd1992} that the 
angular dispersion of emitted electrons is nearly isotropic. This 
behavior is thought to be caused by the insignificant angular anisotropy 
of sub--50--eV yield. 
A typical value for the ejection angle considered in the literature is 
$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
it is quite correct in the range of validity of the first Born 
approximation for any target. However, when a distorted wave approximation 
is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
in the intermediate energy region, as shown in Fig.~\ref{fig:emittedang}.
The higher the charge $Z$, the smaller 
$\overline{\theta}$ will be. Of course, this effect only holds at 
intermediate energies and not at high impact energies.

@@

\begin{table*}[t!]
\begin{center}
\begin{tabular}{|p{0.08\textwidth}|p{0.05\textwidth}|p{0.05\textwidth}|p{
0.05\textwidth}|p{0.05\textwidth}|p{0.19\textwidth}|}
\hline
Element & C & H & N & O & New stoichiometry \\
\hline
Adenine & +0.32 & +0.23 & --0.55 &       & 
C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
\hline
Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
C$_{3.93}$H$_{4.79}$N$_{3.14}$O$_{1.13}$ \\ 
\hline
Guanine & +0.46 & +0.20 & --0.58 & --0.36 & 
C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
\hline
Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
C$_{4.95}$H$_{5.81}$N$_{2.13}$O$_{2.13}$ \\ 
\hline
Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
C$_{3.92}$H$_{3.78}$N$_{2.15}$O$_{2.12}$ \\ 
\hline
\end{tabular}
\caption{Average effective Mulliken charge per atom $q_{\alpha}$, and 
new stoichiometric formula defined by Eq.~(\ref{eq:newstoi}) for five 
DNA molecules.}
\label{tab:newstoi}
\end{center}
\end{table*}

@@

\bibitem{Rudd1992} 
M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
%Electron production in proton collisions with atoms and molecules: energy distributions. 
Rev. Mod. Phys. \textbf{64}, 44--490 (1992).

>>>>

For low energy electron emission, the angular dispersion is nearly 
isotropic~\cite{Rudd1992}.
A typical value for the ejection angle considered in the literature is 
$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
it is quite correct in the range of validity of the first Born 
approximation for any target. However, when a distorted wave approximation 
is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
in the intermediate energy region, as shown in Fig.~\ref{fig:emittedang}.
The higher the charge $Z$, the smaller 
$\overline{\theta}$ will be. Of course, this effect only holds at 
intermediate energies and not at high impact energies.

@@

\begin{table*}[t]
\begin{center}
\begin{tabular}{|p{0.08\textwidth}|p{0.05\textwidth}|p{0.05\textwidth}|p{
0.05\textwidth}|p{0.05\textwidth}|p{0.19\textwidth}|}
\hline
Element & C & H & N & O & New stoichiometry \\
\hline
Adenine & +0.32 & +0.23 & --0.55 &       & 
C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
\hline
Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
C$_{3.93}$H$_{4.79}$N$_{3.14}$O$_{1.13}$ \\ 
\hline
Guanine & +0.46 & +0.20 & --0.58 & --0.36 & 
C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
\hline
Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
C$_{4.95}$H$_{5.81}$N$_{2.13}$O$_{2.13}$ \\ 
\hline
Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
C$_{3.92}$H$_{3.78}$N$_{2.15}$O$_{2.12}$ \\ 
\hline
\end{tabular}
\caption{Average effective Mulliken charge per atom $q_{\alpha}$, and 
new stoichiometric formula defined by Eq.~(\ref{eq:newstoi}) for five 
DNA molecules.}
\label{tab:newstoi}
\end{center}
\end{table*}

@@

\bibitem{Rudd1992} 
M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
%Electron production in proton collisions with atoms and molecules: energy distributions. 
Rev. Mod. Phys. \textbf{64}, 441--490 (1992).
